---
title: "RWorksheet_Punay#2"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#1 
#a.
seq (-5, 5)
```

The output is generated numeric vector containing the integers from -5 to 5, in ascending order

```{r}
#b.
x <- 1:7
x
```
```{r}
#2.
myvector <- seq(1, 3, by=0.2) 
myvector
```
The output includes all values from 1 up to and including 3, where each subsequent value is 0.2 greater than the previous one.

```{r}
#3.
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27,
22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35,
24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26,
18) 

#a
age[3]
#b
age [c(2,4)]
#c
age[-1]

```

```{r}
#4.
x <- c("first"=3, "second"=0, "third"=9)
names(x)
x[c("first", "third")]
```

```{r}
#4.
x <- c("first"=3, "second"=0, "third"=9)
names(x)
x[c("first", "third")]
```

```{r}
#5.
x <- -3:2
x
x[2] <- 0
x

```

The output of the 2nd element changed and modified into 0

```{r}
#6.
month <- c('Jan', 'Feb', 'March', 'Apr', 'May', 'June')
price <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
liters <- c(25, 30, 40, 50, 10, 45)

fuel <- data.frame(month, price, liters)
fuel
avg <- weighted.mean(liters, price)
avg

```
```{r}
#7.
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers),
sd(rivers), min(rivers), max(rivers))
data

```


```{r}
#8.
#a.
rank <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25)

celeb <- c('Tom Cruise','Rolling Stones','Oprah Winfrey','U2','Tiger Woods',
           'Steven Spielberg','Howard Stern','50 Cent','Cast of the Sopranos','Dan Brown',
           'Bruce Springsteen','Donald Trump','Muhammad Ali','Paul McCartney','George Lucas',
           'Elton John','David Letterman','Phil Mickelson','J.K Rowling','Bradd Pitt',
           'Peter Jackson','Dr. Phil McGraw','Jay Leno','Celine Dion','Kobe Bryant')

pay <- c(67,90,225,110,90,332,302,41,52,88,55,44,55,40,223,34,40,47,75,25,39,45,32,40,31)


forbes <- data.frame (rank,celeb,pay)
forbes

#b.
forbes$rank[forbes$celeb=="J.K Rowling"] <- 15
forbes$pay[forbes$celeb=="J.K Rowling"] <- 90

forbes[forbes$celeb=="J.K Rowling",]
```

C.

The dataset lists 25 celebrities (celeb), each with a corresponding rank (1 to 25) and their pay (in millions, presumably).

The rank reflects their position on a list of highest-paid or most influential celebrities.

The pay column shows how much each celebrity earned in a given time period.















