---
title: "RWorsheet_Punay#4a"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




#1
```{r}
#a.
shoe_size <- c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0 ,11.5, 8.5, 5.0, 10.0, 65, 75, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)

height <- c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)

gender <- c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M", "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")



daf <- data.frame(shoe_size, height, gender)
daf

```
The dataset contains 24 observations and 3 variables:

Shoe size: Numeric (range = 5.0 to 13.0)

Height: Numeric (range = 59.0 to 77.0 inches)

Gender: Categorical (F or M)

It represents shoe sizes and corresponding heights for male and female respondents.



```{r}
#b.
male_data <- subset(daf, gender == "M")
female_data <- subset(daf, gender == "F")

male_data
female_data


```




```{r}
#c. 
mean_shoe <- mean(daf$shoe_size)
mean_height <- mean(daf$height)

mean_shoe
mean_height
```
```{r}
#d.
cor(daf$shoe_size, daf$height)
```
There is no significant relationship between shoe size and height based on this dataset (r = -0.1622).




#2
```{r}
#d.
months <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August",
"July","December","August","August","September","November","February","April")

factor_months_vector <- factor(months)
factor_months_vector

```




#3
```{r}
summary(months)
summary(factor_months_vector)

```

'factor_months_vector' shows frequency counts for each category while
'months' just tells you length/type.




#4
```{r}
direction <- c("East", "West", "West", "West", "West", "North", "North", "North")
factor_direction <- factor(direction)
new_order_data <- factor(factor_direction, levels = c("East", "West", "North"))
print(new_order_data)

```



#5
```{r}
data <- read.table("import_march.csv", header = TRUE, sep = ",")
data
```



#6
```{r}

exhaustive_search <- function(x) {
 
  if (is.na(x)) {
    print("Invalid input")
    return(invisible(NULL))
  }
  
  
  if (x < 1 || x > 50) {

    cat("The number selected is beyond the range of 1 to 50\n")
    return(invisible(NULL))
  }
  
  found <- FALSE
  for (i in 1:50) {
    if (i == x) {
      found <- TRUE
     
      if (i == 20) {
        print(TRUE)
      } else {
        print(i)
      }
      break   
    }
  }
  
  if (!found) {
   
    cat("Number not found in the set 1:50\n")
  }
}


user_in <- as.integer(readline(prompt = "Enter a number (can be any integer): "))
exhaustive_search(user_in)


```


#7
```{r}
#Function
min_bills <- function(price) {
 
  if (is.na(price)) {
    print("Invalid input. Please enter a numeric value divisible by 50.")
    return()
  }
  
  # Check price
  if (price %% 50 != 0) {
    print("The price must be divisible by 50.")
  } else if (price < 50) {
    print("The price must be at least 50 pesos.")
  } else {
    # Initialize 
    n1000 <- price %/% 1000
    price <- price %% 1000
    
    n500 <- price %/% 500
    price <- price %% 500
    
    n200 <- price %/% 200
    price <- price %% 200
    
    n100 <- price %/% 100
    price <- price %% 100
    
    n50 <- price %/% 50
    
    total_bills <- n1000 + n500 + n200 + n100 + n50
    
    cat("Minimum number of bills needed:", total_bills, "\n")
    cat("Breakdown:\n")
    cat("₱1000:", n1000, "\n")
    cat("₱500 :", n500, "\n")
    cat("₱200 :", n200, "\n")
    cat("₱100 :", n100, "\n")
    cat("₱50  :", n50, "\n")
  }
}

# int main hahahaha
snack_price <- as.integer(readline(prompt = "Enter the price of the snack (divisible by 50): "))

min_bills(snack_price)

```




#8
```{r}
#a
Name <- c("Annie", "Thea", "Steve", "Hanna")
Grade1 <- c(85, 65, 75, 95)
Grade2 <- c(65, 75, 55, 75)
Grade3 <- c(85, 90, 80, 100)
Grade4 <- c(100, 90, 85, 90)


df <- data.frame(Name, Grade1, Grade2, Grade3, Grade4)
df

```




```{r}
#b.

avg_Annie <- (df$Grade1[1] + df$Grade2[1] + df$Grade3[1] + df$Grade4[1]) / 4
if (avg_Annie >= 90) {
  print(paste(df$Name[1], "'s average grade this semester is", avg_Annie))
}

avg_Thea <- (df$Grade1[2] + df$Grade2[2] + df$Grade3[2] + df$Grade4[2]) / 4
if (avg_Thea >= 90) {
  print(paste(df$Name[2], "'s average grade this semester is", avg_Thea))
}

avg_Steve <- (df$Grade1[3] + df$Grade2[3] + df$Grade3[3] + df$Grade4[3]) / 4
if (avg_Steve >= 90) {
  print(paste(df$Name[3], "'s average grade this semester is", avg_Steve))
}

avg_Hanna <- (df$Grade1[4] + df$Grade2[4] + df$Grade3[4] + df$Grade4[4]) / 4
if (avg_Hanna >= 90) {
  print(paste(df$Name[4], "'s average grade this semester is", avg_Hanna))
}
```




```{r}
#c.

avg_Test1 <- (df$Grade1[1] + df$Grade1[2] + df$Grade1[3] + df$Grade1[4]) / 4


avg_Test2 <- (df$Grade2[1] + df$Grade2[2] + df$Grade2[3] + df$Grade2[4]) / 4


avg_Test3 <- (df$Grade3[1] + df$Grade3[2] + df$Grade3[3] + df$Grade3[4]) / 4


avg_Test4 <- (df$Grade4[1] + df$Grade4[2] + df$Grade4[3] + df$Grade4[4]) / 4

msg <- c()

if (avg_Test1 < 80) msg <- c(msg, "The 1st test was difficult")
if (avg_Test2 < 80) msg <- c(msg, "The 2nd test was difficult")
if (avg_Test3 < 80) msg <- c(msg, "The 3rd test was difficult")
if (avg_Test4 < 80) msg <- c(msg, "The 4th test was difficult")

msg  


```




```{r}
#d.

highest_Annie <- df$Grade1[1]
if (df$Grade2[1] > highest_Annie) highest_Annie <- df$Grade2[1]
if (df$Grade3[1] > highest_Annie) highest_Annie <- df$Grade3[1]
if (df$Grade4[1] > highest_Annie) highest_Annie <- df$Grade4[1]
if (highest_Annie > 90) print(paste(df$Name[1], "'s highest grade this semester is", highest_Annie))


highest_Thea <- df$Grade1[2]
if (df$Grade2[2] > highest_Thea) highest_Thea <- df$Grade2[2]
if (df$Grade3[2] > highest_Thea) highest_Thea <- df$Grade3[2]
if (df$Grade4[2] > highest_Thea) highest_Thea <- df$Grade4[2]
if (highest_Thea > 90) print(paste(df$Name[2], "'s highest grade this semester is", highest_Thea))


highest_Steve <- df$Grade1[3]
if (df$Grade2[3] > highest_Steve) highest_Steve <- df$Grade2[3]
if (df$Grade3[3] > highest_Steve) highest_Steve <- df$Grade3[3]
if (df$Grade4[3] > highest_Steve) highest_Steve <- df$Grade4[3]
if (highest_Steve > 90) print(paste(df$Name[3], "'s highest grade this semester is", highest_Steve))


highest_Hanna <- df$Grade1[4]
if (df$Grade2[4] > highest_Hanna) highest_Hanna <- df$Grade2[4]
if (df$Grade3[4] > highest_Hanna) highest_Hanna <- df$Grade3[4]
if (df$Grade4[4] > highest_Hanna) highest_Hanna <- df$Grade4[4]
if (highest_Hanna > 90) print(paste(df$Name[4], "'s highest grade this semester is", highest_Hanna))



```





