---
title: "RWorksheet_Puany#3b"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1
```{r}
#a.
Respondents <- c(1:20)
Sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
Fathers_Occupation <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
Persons_at_Home <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6)
Siblings_at_School <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
Types_of_Houses <- c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)

dats <- data.frame(Respondents, Sex, Fathers_Occupation, Persons_at_Home, Siblings_at_School, Types_of_Houses)

dats
```
```{r}
#b
str(dats)
```
```{r}
summary(dats)
```
```{r}
#c
mean(dats$Siblings_at_School)
```
No it's not

```{r}
#d
dats[1:2, ]
```
```{r}
#e
dats[c(3,5), c(2,4)]

```
```{r}
#f
types_houses <- dats$Types_of_Houses
types_houses
```

```{r}
#g
subset(dats, Sex == 1 & Fathers_Occupation == 1)

```
There are no male respondents whose father is a farmer.

```{r}
#h
subset(dats, Sex == 2 & Siblings_at_School >= 5)

```

#2
```{r}

df = data.frame(Ints=integer(),

Doubles=double(), Characters=character(),
Logicals=logical(),
Factors=factor(),
stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))

```
The structure of the data frame is empty, 0 observation/rows and 5 variable/columns with different data types but has 0 data.


#3
```{r}

Respondents <- c(1:10)
Sex <- c('Male', 'Female', 'Female', 'Male', 'Male', 'Female', 'Female', 'Male', 'Female', 'Male')
Fathers_Occupation <- c(1,2,3,3,1,2,2,3,1,3)
Persons_at_Home <- c(5,7,3,8,6,4,4,2,11,6)
Siblings_at_School <- c(2,3,0,5,2,3,1,2,6,2)
Types_of_houses <- c('Wood','Concrete','Concrete','Wood', 'Semi-concrete', 'Semi-concrete', 'Wood', 'Semi-concrete', 'Semi-concrete', 'Concrete')

HouseholdData  <- data.frame(Respondents, Sex, Fathers_Occupation, Persons_at_Home, Siblings_at_School, Types_of_houses)

write.csv(HouseholdData, file = "HouseholdData.csv", row.names = FALSE)
```


```{r}
#a.
datf <- read.csv("HouseholdData.csv")
datf

```
```{r}
#b.
datf$Sex <- factor(datf$Sex, levels = c("Male", "Female"), labels = c(1, 2))

datf$Sex <- as.integer(as.character(datf$Sex))
datf$Sex

```

```{r}
#c.
datf$Types_of_houses <- factor(datf$Types_of_houses, levels = c("Wood", "Concrete", "Semi-concrete"), labels = c(1, 2, 3))

datf$Types_of_houses <- as.integer(as.character(datf$Types_of_houses))

datf$Types_of_houses
```

```{r}
#d.
datf$Fathers_Occupation <- factor(datf$Fathers_Occupation, levels = c(1, 2, 3), labels = c("Farmer", "Driver", "Others"))

print(datf$Fathers_Occupation)
```

```{r}
#e.
subset(datf, Sex == 2 & Fathers_Occupation == "Driver")

```
```{r}
#e.
subset(datf, Siblings_at_School >= 5)


```

#14
Over the span of July 14–21, 2020, Twitter users were mostly sharing negative sentiments. Also, tweet activity dipped on July 20 across all sentiment types. This pattern may reflect public reaction to key events, with emotional intensity peaking on July 15 and July 21, and dipping on July 20. 
